Theoretical Impulse Response Functions

### 2018-04-03 Latex/Interpretation_Theoretical_IRFs/Interpretation_Theoretical_IRFs.tex
More work on IRFs latex

\section{Positive Balanced-Growth Path - Temporary Shock}

@@

\section{Positive Balanced-Growth Path - Permanent Shock}

>>>>

\section{Positive Balanced-Growth Path - Level Shock}

@@

\section{Positive Balanced-Growth Path - Trend Shock}

Define $x_t$ as the value of variable $x$ at time $t$. Define $\tilde{x}_t$ as the value of $x$ when divide by the value of an exogenous process which is growing at the same rate of $x$. Formally,
$$
\tilde{x}_t = \frac{x_t}{G_{t-1}}
$$
where $G_{t-1}$ may represent the value of the exogenous productivity process which is growing at the same rate of $x$. Define $\tilde{x}$ as the value of $\tilde{x}_t$ when the system is growing at the balanced growth at the BGP without any past or present source of perturbation. In this case, impulse response functions are percentage deviation of $\tilde{x}_t$ from its steady state value $\tilde{x}$. Formally,
\begin{eqnarray}
\begin{aligned}
IRF(\tilde{x}_{t+h} | \varepsilon) &= \log \bigg[ \Pi_{i=0}^h \bigg( \frac{\tilde{x}_{t+i}(\varepsilon)}{\tilde{x}_{t+i-1}(\varepsilon)}  \frac{G_{t+i-1}}{G_{t+i-2}}  \bigg) \bigg]  \\
&= \log \Bigg[ \Pi_{i=0}^h \Bigg( \frac{\frac{x_{t+i}(\varepsilon)}{G_{t+i-1}(\varepsilon)}}{\frac{x_{t+i-1}(\varepsilon)}{G_{t+i-2}(\varepsilon)}}  \frac{G_{t+i-1}(\varepsilon)}{G_{t+i-2}(\varepsilon)}  \Bigg) \Bigg]  \\
&= \log \Bigg[ \Pi_{i=0}^h \Bigg( \frac{x_{t+i}(\varepsilon)}{x_{t+i-1}(\varepsilon)}   \Bigg) \Bigg]  \\
&= \log \bigg( \frac{x_{t+h}(\varepsilon)}{x_{t-1}}  \bigg)  \\
\end{aligned}
\end{eqnarray}
